Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-04 docs/ms.tex
Update ms.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Hierarchical Inference in Weak Lensing: Inferring Pr(e)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A typical procedure of weak lensing analysis  includes ellipticity
measurement,shear inference and mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infer shear from galaxy
ellipticity in a hierachical way.Therefore in our simulation we merely
set up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
acting on one all the galaxies in sky patch,

@@

However in our hierachical Bayesian approach we are able to obtain
the posterior distribution of g ,based on the assumption $\phi$ has
a uniform distribution and galaxies in different sky patches have
the same intrinsic shape distribution.

@@

\subsection{Bias Test}
In this section,we measured the levels of possible systemmatical
bias of this Hierachical inference method.In principle given the correct model and prior ,
the hierchical Bayesian inference method would have no bias,if propagate the whole likelihood function.
However,in practical,the bias may be introduced by the model we use for the intrinsic shape distribution,
and the prior regularizer of the prefactor $\xi$ as well as the Gaussian approximation we did for the likelihood
function of $\vec{g}$ .Therefore a bias test is necessary to identify how much bias there is. 
Following Heymans et al. (2006), we quantify the systematic bias in
in terms of the multiplicative error m and additive error c on the
true shear $g^{true}$ 
\begin{equation}
\hat{g_{i}}-g_{i}^{true}=m_{i}g_{i}^{true}+c_{i}
\end{equation}

@@

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error will
affect the variance and bias of this Hierarchy Bayesian method.
In principle,if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
However,due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$ .
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
The result of bias test and mean square error test is shown in...

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% hierarchical Inference in Weak Lensing: Inferring Pr(e)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A typical procedure of weak lensing analysis  includes ellipticity
measurement,shear inference and mass profile reconstruction. The measurement
of galaxy shapes is the first step of weak gravitational lensing analysis,since
it's the direct observable that relates with tangential shear.However
in this paper we only concern about how to infer shear from galaxy
ellipticity in a hierarchical way.Therefore in our simulation we merely
set up a simple toy model in which we have the observed ellipticity as
data,and the only measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity.We also suppose there is a uniform shear
acting on one all the galaxies in sky patch,

@@

However in our hierarchical Bayesian approach we are able to obtain
the posterior distribution of g ,based on the assumption $\phi$ has
a uniform distribution and galaxies in different sky patches have
the same intrinsic shape distribution.

@@

\subsection{Bias Test}
In this section,we measured the levels of possible systemmatical
bias of this Hierarchical inference method.In principle given the correct model and prior ,
the hierchical Bayesian inference method would have no bias,if propagate the whole likelihood function.
However,in practical,the bias may be introduced by the model we use for the intrinsic shape distribution,
and the prior regularizer of the prefactor $\xi$ as well as the Gaussian approximation we did for the likelihood
function of $\vec{g}$ .Therefore a bias test is necessary to identify how much bias there is. 
Following Heymans et al. (2006), we quantify the systematic bias in
in terms of the multiplicative error m and additive error c on the
true shear $g^{true}$ 
\begin{equation}
\hat{g_{i}}-g_{i}^{true}=m_{i}g_{i}^{true}+c_{i}
\end{equation}

@@

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error will
affect the variance and bias of this Hierarchical Bayesian method.
In principle,if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation ().
However,due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$ .
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
The result of bias test and mean square error test is shown in...
